Mendelian randomization for causal inference in genome-wide association studies

### 2022-03-01 mr-review.Rmd
added text  for berzuini et al (Bayesian Mimr)

>>>>

@berzuini_bayesian_2020 proposed a Bayesian approach to MR where SNP instruments
are permitted to exhibit pleiotropic effects on the outcome. Working in the setting of 
one-sample MR with individual-level data, they construct their 
model with a shrinkage prior, so that many SNP instruments have no horizontal pleiotropic effects. Their 
method relaxes the exclusion restriction assumption to permit horizontal pleiotropy (for some SNP 
instruments) and permits correlated SNP instruments, unlike many frequentist methods. Posterior inference 
proceeds by Markov chain monte carlo sampling. They also elaborate their model for 
a univariate exposure into that for a bivariate exposure to analyze the causal effects of body mass index and serum phenylalanine levels on blood pressure.
